---
output:
  md_document:
    variant: markdown_github
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path =  "figure-markdown_github/")
```


#nmelectiondatr

##An R data package containing general election results for the state of New Mexico (2014+)

This package provides access to data ... General election results for federal, legislative, and statewide offices.     


Data included in the package have been scraped from thousands of PDFs made available via the official site of the [New Mexico State Legislature](https://www.nmlegis.gov/Legislation/Legislation_List).  A full code-through of the scraping & summary processes is available  [here](https://github.com/jaytimm/nmlegisdatr/blob/master/data-raw/scrape_nmsl_data.md).

Scraped from the New Mexico Secretary of State website.

A companion package to `nmlegisdatr`.

##Installation
```{r eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
library(devtools)
devtools::install_github("jaytimm/nmelectiondatr")
library(nmelectiondatr)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
library(nmelectiondatr)
library(tidyverse)
```



##Usage

The package contains six data tables; their contents are summarized in the table below.

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
Table <- c('nmel_pol_geos',
           'nmel_results_county',
           'nmel_results_district',
           'nmel_results_precinct')

Contents <- c('All introduced legislation, including bill id, title, and bill description',
                 'All legislators in both chambers, including party affiliation and legislative district',
                 'Roll calls for all legislation reaching either chamber for vote',
                 'Sponsors for each bill',
                 'Roll call results, including results disaggregated by political affiliation',
                 'Votes cast, atttendance rates, and party loyalty rates for all legislators')

kable(data.frame(cbind(Table, Contents)))
```


Tables can also be viewed as a [collection of CSVs](https://github.com/jaytimm/nmlegisdatr/tree/master/nmsl_tables/CSVs) or as individual tabs in a single [Excel file](https://github.com/jaytimm/nmlegisdatr/tree/master/nmsl_tables/excel).


