---
output:
  md_document:
    variant: markdown_github
---


This could likely be a table.

```{r}
#2018---
nm_hds_2018 <- "http://electionresults.sos.state.nm.us/resultsSW.aspx?type=LGX&map=CTY&lValue=100&gValue=001"
nm_fed_2018 <- 'http://electionresults.sos.state.nm.us/resultsSW.aspx?type=FED&map=CTY'
nm_state_2018 <- 'http://electionresults.sos.state.nm.us/resultsSW.aspx?type=SW&map=CTY'


#2016---
nm_hds_2016 <- 'http://electionresults.sos.state.nm.us/resultsSW.aspx?eid=84&type=RPX&map=CTY'
nm_sds_2016 <- 'http://electionresults.sos.state.nm.us/resultsSW.aspx?eid=84&type=SNX&map=CTY'
nm_fed_2016 <- 'http://electionresults.sos.state.nm.us/resultsSW.aspx?eid=84&type=FED&map=CTY'
nm_state_2016 <- 'http://electionresults.sos.state.nm.us/resultsSW.aspx?eid=84&type=SW&map=CTY'


#2014---
nm_hds_2014 <- 'http://electionresults.sos.state.nm.us/resultsSW.aspx?eid=2&type=LGX&map=CTY&lValue=100&gValue=001'
nm_fed_2014 <- 'http://electionresults.sos.state.nm.us/resultsSW.aspx?eid=2&type=FED&map=CTY'
nm_state_2014 <- 'http://electionresults.sos.state.nm.us/resultsSW.aspx?eid=2&type=SW&map=CTY'


#Totals---
all_sos_links <- c(nm_hds_2018, nm_fed_2018, nm_state_2018,
                   nm_hds_2016, nm_sds_2016, nm_fed_2016, nm_state_2016,
                   nm_hds_2014, nm_fed_2014, nm_state_2014)
```




Simple eid--year crosswalk.

```{r}
yearcross <- data.frame(eid = c('2', '84'), year = c('2014', '2016'),
                        stringsAsFactors = FALSE)
```


Some base-r functions.

```{r}
fill_down <- function(z) { 
  y <- c(NA, head(z, -1))
  z <- ifelse(is.na(z), y, z)
  if (any(is.na(z))) Recall(z) else z }

winner <- function(x) {
  y <- rep('', length(x))
  y[which.max(x)] <- 'Winner'
  y}
```




```{r eval=FALSE}
library(XML)

nmsl_get_vote_results <- function(link) {

  #Step 0. Get year.
  year <- ifelse(length(grep('eid', link))==1, '1', '2018')
  
  if (year == '1') {
    eid <- gsub('(^.*eid=)([0-9]+)(&.*$)', '\\2', link)
    year <- yearcross[yearcross==eid ,]$year  
    eid <- paste0('&eid=',eid)
     } else {
      eid <-''}
    
    
  #Step 1. Scrape web.
  x <- XML::readHTMLTable(link, 
                        as.data.frame=TRUE, 
                        stringsAsFactors=FALSE) 
  
  #Step 2. Get metadata.
  keys <- x[["MainContentxuwgResults_main"]][c(2, 3, 7, 13)] 
  keys <- keys[grepl('Follow this', keys$V2),]
  Encoding(keys$V2) <- 'UTF-8'
  keys$V2 <- gsub('Follow .*$', '', keys$V2)
  
  keys$V2 <- gsub('[^[:alnum:] -]', '', keys$V2)
  keys$V2 <- trimws(keys$V2)
  

  keys$id <- c(1:nrow(keys))
  keys$type_name <- gsub(' -.*$', '', keys$V2)
  keys$geo_name <- gsub('^.* - ', '', keys$V2)

  keys <- keys[, c(6, 5, 7, 2:4)]
  colnames(keys)[4:6] <- c('rid', 'osn', 'type')

  
  #Step 3. Build link.
  keys$link <- paste0('http://electionresults.sos.state.nm.us/ResultsExport.aspx?rid=', keys$rid, '&osn=', keys$osn, '&pty=&name=', gsub(' ', '%20', keys$type_name), '&cat=CTYALL', eid)
  
  keys$Year <- year
  keys <- keys[, c(8,2,1,3,7)]
  keys <- keys[!grepl('retention|amendment|bond', tolower(keys$type_name)),] #Remove questions.
  
  #Step 4. 
  olnasty <- x[["MainContentxuwgResults_main"]][c(3,4,14)] 
  Encoding(olnasty$V3) <- 'UTF-8'

  olnasty <- olnasty[complete.cases(olnasty), ]
  olnasty <- olnasty[!grepl('^Total|^[0-9]', olnasty$V3),]
  olnasty <- olnasty[grepl('^[A-Z]', olnasty$V3),]

  olnasty$id <- c(1:nrow(olnasty))
  olnasty$id <- ifelse(olnasty$id %in% grep('Candidate', olnasty$V3), olnasty$id, NA)

  olnasty$id <- fill_down(olnasty$id)
  olnasty <- subset(olnasty, V3 != 'Candidate')
  olnasty <- within(olnasty, id <- match(olnasty$id, unique(olnasty$id)))

  olnasty <- olnasty[, c(4,1,3,2)]
  colnames(olnasty) <- c('id','Candidate', 'Party', 'Votes')
  olnasty$Votes <- as.numeric(gsub(',', '', olnasty$Votes))

  olnasty$Winner <- unlist(tapply(olnasty$Votes, olnasty$id, winner))
  olnasty$Year <- year
  
  #Add type_name & geo_name via id column.
  olnasty <- merge(olnasty, keys[, c(1:4)])
  olnasty <- olnasty[, c(2,7:8,1,3:6)]
  keys <- keys[, c(1,3:5)]
  
  #Step 5. Output data as list.
  out <- list("Results" = olnasty, "Meta" = keys)
  return(out)
}
```



```{r eval=FALSE, message=FALSE, warning=FALSE}
elections_summary <- lapply(all_sos_links, nmsl_get_vote_results)

library(tidyverse)
full_meta <- lapply(elections_summary, '[[', 2) %>%
  bind_rows()

full_results <- lapply(elections_summary, '[[', 1) %>%
  bind_rows()
```


Address some encoding issues.  Not a fantastic solution.
```{r eval=FALSE}
full_results$Candidate <- gsub('\\.', '',  full_results$Candidate) #Periods
full_results$Candidate <- gsub('\"', '\'', full_results$Candidate)

full_results$Candidate [grep('LORENZO', full_results$Candidate)] <- 'LORENZO A LARRA\u00D1AGA'
full_results$Candidate [grep('BRIAN S', full_results$Candidate)] <- 'BRIAN S COL\u00D3N'
full_results$Candidate [grep('JOHNNY', full_results$Candidate)] <- 'JOHNNY F LU\u00C9VANO JR'
full_results$Candidate [grep('COFFEY', full_results$Candidate)] <- 'ROBERT M COFFEY JR'
full_results$Candidate [grep('GEORGE DODGE', full_results$Candidate)] <- 'GEORGE DODGE JR'
full_results$Candidate [grep('ALFRED GORDON', full_results$Candidate)] <- 'ALFRED GORDON GLASS JR'
```



Get election results.  where 'x' is a link based on 'keys' table.  As opposed to hand-built table that includes leg house districts, fed house & senate.  

```{r eval=FALSE}
library(httr)
library(readxl) 

nmsl_get_precinct_data <- function(x) {
  
  #Step 1.
    tmp <- tempfile()
    filename <- paste0(tmp,'.xlsx')
    httr::GET(x, write_disk(filename))
    sheets <- readxl::excel_sheets(filename)

  #Step 2.
    z <- lapply(sheets, 
                function(y) 
                  readxl::read_excel(filename,
                                     sheet = y, 
                                     col_names = TRUE, 
                                     skip = ifelse(grepl('State', x), 6, 5))) 
  #Step 3. Re-do with Base-R.
    names(z) <- sheets  
    z <- bind_rows(z, .id = 'geo1') %>%
      mutate(geo2 = ifelse(is.na(County), Precinct, County)) %>%
      select(-County, -Precinct) %>%
      select(geo1, geo2, everything()) %>%
      gather(key = Candidate, value = votes, c(3:ncol(.)))
}
```


Then apply. Per legislative "unit".  Results as a list of dataframes -- each legislative geo as independent df.

```{r eval=FALSE}
elections_nmsos_raw <- lapply(full_meta$link, nmsl_get_precinct_data)

names(elections_nmsos_raw) <- paste0(full_meta$Year, '-',full_meta$type_name, '-', full_meta$geo_name)

elections_nmsos <- bind_rows(elections_nmsos_raw, .id = 'govt') %>%
  separate(govt, c('Year', 'type_name', 'geo_name'), '-') %>%
  mutate(Candidate = gsub('\\.', '', Candidate)) %>%
  mutate(Candidate = gsub('\"', '\'', Candidate)) %>%
  left_join(full_results %>% select(Year, type_name, geo_name, Candidate, Party))

#"(TED) THEODORE BARELA", "'ROCKY' ROQUE DE LA FUENTE AND MICHAEL STEINBERG"

elections_nmsos$geo1[grep('a Ana',elections_nmsos$geo1)] <- 'Dona Ana'
elections_nmsos$geo2[grep('a Ana',elections_nmsos$geo2)] <- 'Dona Ana'
```

Add GEOIDs -- ?  


Includes all statewide/federal/state legslative races at the precinct level. 

```{r}
nmel_results_precinct <- elections_nmsos %>%
  filter(grepl('PRE|PCT|^[0-9]|Precinct', geo2)) %>%
  mutate(geo1 = trimws(gsub(' - .*$', '', geo1)),
         geo2 = (as.numeric(gsub('[^0-9]' ,'', geo2))),
         geo_name = gsub('^DISTRICT |^District ', '', geo_name))#%>%
  #rename(prec_num = geo, county_name = vote_type)

colnames(nmel_results_precinct) <- c('Year','Type', 'Type_Sub', 'County_Name', 'Precinct_Num', 'Candidate', 'Votes', 'Party')
```



Includes NM state legislature races aggregated to nm congressional districts. Disaggregated by Early/Absentee/ElectionDay.

```{r}
nmel_results_district <- elections_nmsos %>%
  filter(grepl('State Representative|State Senator', type_name) &
           grepl('County Results - ', geo1) & geo2 == 'TOTALS') %>%
  mutate(geo_name = gsub('^DISTRICT |^District ', '', geo_name)) %>%
  mutate(cast = gsub('County Results - ', '', geo1)) %>%
  select(-geo1,-geo2)

colnames(nmel_results_district) <- c('Year','Type', 'NAME', 'Candidate', 'Votes', 'Party', 'Cast')
```



Includes state-wide/federal races aggregated at the county level. At-large races. Disaggregated by Early/Absentee/ElectionDay.

```{r}
nmel_results_county <- elections_nmsos %>%
  filter(!grepl('State Representative|State Senator|Representative', type_name) &
           grepl('County Results - ', geo1))%>%
  mutate(cast = gsub('County Results - ', '', geo1))%>%
  select(-geo1, -geo_name) %>%
  rename(NAME = geo2)

colnames(nmel_results_county) <- c('Year','Type', 'NAME', 'Candidate', 'Votes', 'Party', 'Cast')
```


```{r}
nmel_results_summary <- full_results %>%
  select(-id)%>%
  mutate(geo_name = gsub('^DISTRICT |^District ', '', geo_name)) %>%
  group_by(Year, type_name, geo_name) %>%
  mutate(Percent = round(Votes/sum(Votes),3)) %>%
  select(Year:Votes, Percent, Winner)%>%
  ungroup()

colnames(nmel_results_summary) <- c('Year','Type', 'Type_Sub', 'Candidate', 'Party', 'Votes', 'Percent', 'Winner')
```



###6. Output, etc. 

STILL need to output full_results.

```{r eval=FALSE, include=FALSE}
setwd("C:\\Users\\jason\\Google Drive\\GitHub\\packages\\nmelectiondatr")
devtools::use_data(nmel_results_summary, overwrite=TRUE)
devtools::use_data(nmel_results_precinct, overwrite=TRUE)
devtools::use_data(nmel_results_district, overwrite=TRUE)
devtools::use_data(nmel_results_county, overwrite=TRUE)
```



```{r eval=FALSE, include=FALSE}
#Output to single xl file.
setwd("C:\\Users\\jason\\Google Drive\\GitHub\\packages\\nmelectiondatr\\nmelection_tables\\excel")
library(writexl) #Lovely package.

out <- list('nmel_results_summary' = nmel_results_summary,
            'nmel_results_precinct' = nmel_results_precinct, 
            'nmel_results_district' = nmel_results_district, 
            'nmel_results_county' = nmel_results_county)
writexl::write_xlsx(out, 'nmelectiondatr.xlsx')

#Perhaps as CSVs as well.  Allow for investigation via github.
```


```{r eval=FALSE, include=FALSE}
#Output to CSVs to link as examples in Demo.
setwd("C:\\Users\\jason\\Google Drive\\GitHub\\packages\\nmelectiondatr\\nmelection_tables\\CSVs")
write.csv(nmel_results_precinct, 'nmel_results_precinct.csv' , row.names=FALSE)
write.csv(nmel_results_district, 'nmel_results_district.csv' , row.names=FALSE)
write.csv(nmel_results_county, 'nmel_results_county.csv' , row.names=FALSE)
write.csv(nmel_results_summary, 'nmel_results_summary.csv' , row.names=FALSE)
```


Output consists of six tables, which are made available in three different formats:

* As data frames in the `nmlegisdatr` R package
* As a [collection of CSVs](https://github.com/jaytimm/nmlegisdatr/tree/master/nmsl_tables/CSVs)
* As tabs in a single [excel file](https://github.com/jaytimm/nmlegisdatr/tree/master/nmsl_tables/excel)









